Combinatorics of the geometry of Wilson loop diagrams

### 2019-02-04 General WLD combinatorics.tex
Signed-off-by: Amasus <susama@alum.mit.edu> changed definitions in secton 3.2, as discussed wtih Karen

%*****************
%Shortcuts for frequently used special characters
\newcommand{\fB}{\mathfrak{B}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\fZ}{\mathfrak{Z}}
\newcommand{\cM}{\mathcal{M}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cI}{\mathcal{I}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\G}{\mathbb{G}}
\newcommand{\Prop}{\textrm{Prop}}
\newcommand{\cW}{\mathcal{W}}
\newcommand{\bM}{\mathbb{M}}
\newcommand{\cZ}{\mathcal{Z}}
\newcommand{\cY}{\mathcal{Y}}
\newcommand{\Dom}{\textrm{Dom}}
\newcommand{\detzr}[1] {\langle (\cZ_*^\mu|V(p))^{#1} \rangle}
\newcommand{\II}{\mathcal{I}}
\newcommand{\PP}{\mathcal{P}}
\newcommand{\BB}{\mathcal{B}}
\newcommand{\CS}{\mathcal{S}}
\newcommand{\interval}[2]{[\![#1,#2]\!]}
\newcommand{\gale}[1]{\preccurlyeq_{#1}}
\newcommand{\sgale}[1]{\prec_{#1}}
%*****************

@@

\begin{dfn}\label{WLdfn}
A Wilson loop diagram is given by the following data: a cyclicly ordered set $V$, along with a choice of first vertex (labeled $1$), and $k$ pairs, called propagators, written $\{p_r = (i_r, j_r)\}_{r=1}^k$ with labels ordered such that $i_r +1 < j_r$ relative to the fisrt vertex. \end{dfn}

@@

asdf

@@

\begin{dfn}\label{props inside p}
Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $p = (i,j) \in \cP$ be a propagator. As always, we use the convention $i+1 <_1 j$. The region of $W$ bounded by $p$ and the edge of the Wilson loop diagram from $i$ to $j+1$ is refered to as the region {\bf inside} $p$, and the complement is the region {\bf outside }$p$. The set of propagators inside (resp. outside) $p$ are those lying in the region inside (resp. outside) $p$, excluding $p$ itself.
\end{dfn} \sanote{changed dfn to match notation} \sanote{do we really mean $i$ to $j+1$, or $i+1$ to $j$, as in length}

Note that this depends on the convention that $i+1 <_1 j$: if we work with the $<_j$ order on vertices then the regions inside and outside $p$ are swapped. \sanote{Is this remark needed? or does is obfuscate?}

\begin{dfn}\note{right now this doesn't depend on the order of $i$ and $j$, but that might matter later on?}
Let $p = (i,j) \in cP$ be a propagator in $W$.  Define the \textit{length} of $p$ to be 
\[\ell(p) = min\big\{|[i+1,j]|,|[j+1,i]|\big\}.\]
\end{dfn}
In other words, given that $p$ partitions the vertices of $W$, $\ell(p)$ is the size of the smaller of the two partitions.

>>>>

%*****************
%Shortcuts for frequently used special characters
\newcommand{\fB}{\mathfrak{B}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\fZ}{\mathfrak{Z}}
\newcommand{\cM}{\mathcal{M}}
\newcommand{\cA}{\mathcal{A}}
\newcommand{\cI}{\mathcal{I}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\G}{\mathbb{G}}
\newcommand{\Prop}{\textrm{Prop}}
\newcommand{\cW}{\mathcal{W}}
\newcommand{\bM}{\mathbb{M}}
\newcommand{\cZ}{\mathcal{Z}}
\newcommand{\cY}{\mathcal{Y}}
\newcommand{\Dom}{\textrm{Dom}}
\newcommand{\detzr}[1] {\langle (\cZ_*^\mu|V(p))^{#1} \rangle}
\newcommand{\II}{\mathcal{I}}
\newcommand{\PP}{\mathcal{P}}
\newcommand{\BB}{\mathcal{B}}
\newcommand{\CS}{\mathcal{S}}
\newcommand{\interval}[2]{[\![#1,#2]\!]}
\newcommand{\gale}[1]{\preccurlyeq_{#1}}
\newcommand{\sgale}[1]{\prec_{#1}}
\renewcommand\vec[1]{\overrightarrow{#1}}
\newcommand\cev[1]{\overleftarrow{#1}}
%*****************

@@

\begin{dfn}\label{WLdfn}
A Wilson loop diagram is given by the following data: a cyclicly ordered set $V$, along with a choice of first vertex (labeled $1$), and $k$ pairs, called propagators, written $\{p_r = (i_r, j_r)\}_{r=1}^k$.  \end{dfn}

Generally speaking, the propagators are undirected, so $p = (i,j) = (j,i)$. In order to fix a convention, we write $p = (i,j)$ with  $i +1 < j$ relative to the first vertex. However, at times (section \ref{sec:propagator configs}), we consider directed propagators, where $p= (i,j)$ denotes a particular propagator flowing in one direction, while $p= (j,i)$ denotes the \emph{same} propagators flowing in the opposite direction. \sanote{Addendum 1}

@@

@@

 \sanote{can we use the notation directed propagator here? to emphasize the notational change?}

\begin{dfn}\label{props inside p}
Let $W = (\cP, n)$ be an admissible Wilson loop diagram, and $\vec{p} = (i,j) \in \cP$ be a directional propagator and $\cev{p} = (j,i)$ be the same propagator with the opposite directionality. Call the vertices of $W$ \bas V_{in}(\vec{p}) = \{a \in [n] | i <_i a <_i j\} \cup V(p) \eas the region of $W$ {\bf inside} $\vec{p}$, and \bas V_{out}(\vec{p}) = \{a \in [n] | j <_j a <_j i\} \cup V(p) \;.\eas the region {\bf outside }$\vec{p}$. The set of propagators inside (resp. outside) $\vec{p}$ are those lying in the region inside (resp. outside) are the $q \neq p \in \cP$ such that  $V(q) \subset V_{in}(p)$ (resp. $V(q) \subset V_{out}(p)$) .
\end{dfn}

Note that under this definiton, $V_{in}(\vec{p}) = V_{out}(\cev{p})$ and $V_{out}(\vec{p}) = V_{in}(\cev{p})$. That is, the regions inside and outside of a propagator switch depending on the direction imposed on the propagators $p$.

\begin{dfn}\note{right now this doesn't depend on the order of $i$ and $j$, but that might matter later on?}
Let $p = (i,j) \in cP$ be a propagator in $W$.  Define the \textit{length} of $p$ to be 
\[\ell(p) = min\big\{|V_(in)(\vec{p})|,|V_(in)(\cev{p})|\big\}-2 = min\big\{|[i+1,j]|,|[j+1,i]|\big\}.\]
\end{dfn}
In other words, given that $p$ partitions the vertices of $W$, $\ell(p)$ is the size of the smaller of the two partitions.
